### 2014-01-23 Draft/abstract.tex
Changed Abstract and Intro

\begin{abstract}
Formal specifications of using a libraries Application Programming Interface (API)
can be used in conjunction with formal analysis tools such as
model checkers and runtime verifiers to assess the quality of a software.
Despite being desirable, most API's do not have formal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based automated approach \tool ,
to infer formal specifications from natural language text of API documents.
In particular, we focus on temporal constraints, that are defined as constraints on the
\textit{allowed sequence of invocations of methods within an API}.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of 60\% precision and 80\% recall
in inferring 63 temporal constraints from more than 2400 sentences of API documents.

>>>>

\begin{abstract}
Temporal specifications of an Application Programming
Interface (API) describe allowed sequences of invocations
of methods within an API. Despite being desirable for 
software testing and verification (through formal analysis tools),
most API's do not have formal temporal specifications.
In contrast, API documents contain valuable information about the usage in natural language.
However, formal analysis tools are not designed to work on specifications in natural languages.
Manually writing formal specifications based on natural language text in API documents
can be prohibitively time consuming and error prone.
To address this issue, we propose a natural language processing based automated approach \tool ,
to infer formal temporal specifications from natural language text of API documents.
To evaluate our proposed approach, we applied \tool\ to infer temporal constraints from 
commonly used package \CodeIn{java.io} from JDK API and Amazon S3 REST API.
Our evaluation results show that \tool\ achieves an average of 60\% precision and 80\% recall
in inferring 63 temporal constraints from more than 2400 sentences of API documents.

### 2014-01-23 Draft/introduction.tex
Changed Abstract and Intro

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item A NLP based approach that infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/icon}}. 
	\item An evaluation of proposed approach on Java 7 and Amazon S3 REST API.
\end{itemize}

>>>>

%Use consistent term technique or approach
%Methodology for generating domain dictionaries 
\begin{itemize}
	\item A NLP based approach that infers temporal constraints of method invocations. 
	To the best of our knowledge, our approach is the first one to apply NLP for the goal of inferring temporal specifications from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03,SNLP1}, which is a natural language parser to derive the grammatical structure of sentences.
	An open source implementation of the prototype is publicly available on our project website\footnote{\url{https://sites.google.com/site/icon}}. 
	\item An evaluation of proposed approach on 
commonly used package \CodeIn{java.io} from JDK API and Amazon
S3 REST API. Our evaluation results show that \CodeIn{ICON} achieves
an average of 60\% precision and 80\% recall in inferring 63
temporal constraints from more than 2400 sentences of API
documents.
\end{itemize}
